---
title       : Mosaicing test summary world mosaic
subtitle    : Global assessment interpolation
author      : Benoit Parmentier
job         : NEX job world
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

```{r,echo=F}

#First let's set up the input parameters for the script in R:

in_dir <- "/data/project/layers/commons/NEX_data/mosaicing_data_test/mosaic_world_07012015"

region_name <- "world" #PARAM 13 #reg4 South America, Africa reg5,Europe reg2, North America reg1, Asia reg3
mosaicing_method <- c("unweighted","use_edge_weights")
out_suffix <- paste(region_name,"_","mosaic_07092015",sep="") 
#_mosaic_run10_1500x4500_global_analyses_06212015
day_to_mosaic <- c("20100831",
                   "20100901") #PARAM7

png_files <- mixedsort(list.files(path=in_dir,pattern=paste("*",out_suffix,".png",sep="")))

```

## Mosaicing with two methods

All regions were merged together for the two mosaicing methods:

1. Unweighted mean: each image a pixel has no specific weight
2. distance from edge: weights of pixels depends on distance to edges for each tiles

The world mosaic was produced for two dates:
- 20100831
- 20100901

---

--- .class #id 

<!-- Limit image width and height -->
<style type="text/css">
img {     
  max-height: 560px;     
  max-width: 964px; 
}
</style>
 
<!-- Center image on slide -->
<script type="text/javascript" src="http://ajax.aspnetcdn.com/ajax/jQuery/jquery-1.7.min.js"></script>
<script type="text/javascript">
$(function() {     
  $("p:has(img)").addClass('centered'); 
});
</script>

# Unweighted mean reg: 20100831

```{r, echo=FALSE}
#image_file1 <- file.path(in_dir,"Figure9_clim_mosaics_day_test_unweighted_20100831_world_mosaic_07092015")

fname <- paste("Figure9_clim_mosaics_day_test_unweighted_20100831_",out_suffix,".png",sep="")

image_file1 <- file.path(in_dir,fname)

```

```{r image_file1, echo = F, results = 'asis'}
md_str <- paste('\n![unweighted](',image_file1,')\n',sep="") 
cat(md_str)
```

---

# Edge weigted mean :20100831

```{r, echo=FALSE}
#image_file2 <- file.path(in_dir,"Figure9_clim_mosaics_day_test_edge_weighted_20100831_world_mosaic_07092015.png")


fname <- paste("Figure9_clim_mosaics_day_test_edge_weighted_20100831_",out_suffix,".png",sep="")
image_file2 <- file.path(in_dir,fname)

```

```{r image_file2, echo = F, results = 'asis'}
md_str <- paste('\n![](',image_file2,')\n',sep="") 
cat(md_str)
```

---

# Unweighted mean : 20100901

```{r, echo=FALSE}
#image_file3 <- file.path(in_dir,"Figure9_clim_mosaics_day_test_unweighted_20100901_world_mosaic_07092015.png")

fname <- paste("Figure9_clim_mosaics_day_test_unweighted_20100901_",out_suffix,".png",sep="")

image_file3 <- file.path(in_dir,fname)

#fname <- paste("Figure2_mosaic_mean_unweighted_20100901_unweighted_20100901_20100901_",out_suffix,".png",sep="")
#image_file3 <- file.path(in_dir,fname)

```

```{r image_file3, echo = F, results = 'asis'}
md_str <- paste('\n![](',image_file3,')\n',sep="") 
cat(md_str)
```

---

# Edge weigted mean : 20100901

```{r, echo=FALSE}
#image_file4 <- file.path(in_dir,"Figure9_clim_mosaics_day_test_edge_weighted_20100901_world_mosaic_07092015.png")

fname <- paste("Figure9_clim_mosaics_day_test_edge_weighted_20100901_",out_suffix,".png",sep="")
image_file4 <- file.path(in_dir,fname)

```

```{r image_file4, echo = F, results = 'asis'}
md_str <- paste('\n![](',image_file4,')\n',sep="") 
cat(md_str)
```

---

